\DomainHeader{Data Exchange}{15\%}

\begin{Objectives}
  \item Convert USD assets to common formats (e.g., glTF) and preserve fidelity.
  \item Document conceptual data mappings (e.g., USD $\rightarrow$ MaterialX).
  \item Explain USDC vs USDA trade-offs.
  \item Implement round-trip pipelines to/from a DCC.
  \item Use schemas for nonstandard attributes/structures during import/export.
  \item Write validators for exported USD assets.
  \item Write exporters/converters to USD.
  \item Write or extend USD importers in a DCC.
\end{Objectives}

\begin{Resources}
  \item Learn OpenUSD: Developing Data Exchange Pipelines
  \item OpenUSD tutorials: Traversing a Stage; Converting Between Layer Formats
  \item OpenUSD glossary: Over; Stage Traversal
  \item Technical references: Conceptual Data Mapping; USD FAQ ``What File
        Format Is My .usd File?''; USDZ File Format Specification
  \item Tooling: \texttt{usdchecker}, \texttt{usdcat}, \texttt{usdzip}
  \item OpenUSD API: GetNamespace; ComputeExtentFromPlugins; GetExtentAttr
\end{Resources}

\CheatSheetTitle
\begin{itemize}[leftmargin=*]
  \item \textbf{One scene description, three encodings}: \texttt{.usda} is
        text, \texttt{.usdc} is binary crate, \texttt{.usd} may be
        \emph{either} --- \texttt{usdcat} tells you which.\index{usda}\index{usdc}
  \item \textbf{Choosing}: \texttt{usda} for review, diffs, and debugging;
        \texttt{usdc} for production IO (memory-mapped, lazy, compact);
        \texttt{usdz} is an uncompressed zip \emph{delivery} package --- not an
        editing format.\index{usdz}
  \item \textbf{Exporter skeleton}: traverse $\rightarrow$ filter by schema
        (\texttt{IsA}) $\rightarrow$ map attributes $\rightarrow$ declare
        \texttt{defaultPrim}, \texttt{upAxis}, \texttt{metersPerUnit}.\index{traversal}
  \item \textbf{Traversal skips instances}: \texttt{Traverse()} does not
        descend into instance proxies unless you ask
        (\texttt{Usd.TraverseInstanceProxies}).\index{instance proxy}
  \item \textbf{glTF mapping}: triangulate n-gons; \texttt{primvars:st}
        $\rightarrow$ \texttt{TEXCOORD\_0}; convert up axis and units (glTF is
        Y-up, meters); UsdPreviewSurface $\approx$ PBR metallic-roughness.\index{glTF}
  \item \textbf{Round-trips flatten composition} --- references, variants, and
        payloads bake on export. Import as \texttt{over}s to stay
        non-destructive.\index{round-trip}
  \item \textbf{Nonstandard data}: namespaced custom attributes (a
        \texttt{myStudio:} prefix) or formalized API
        schemas.\index{custom attribute}
  \item \textbf{Validate every export}: \texttt{usdchecker} catches missing
        stage metadata; authored \texttt{extent} on every Boundable is the
        exporter's own job.\index{usdchecker}
\end{itemize}

\section{Core Concepts}

\subsection{What a clean export looks like}\label{sec:de-clean}\objref{4.6, 7.2}
Everything in this chapter revolves around one exemplar --- a minimal asset
the way a well-behaved exporter should write it:

\begin{lstlisting}
#usda 1.0
(
    defaultPrim = "Plate"
    metersPerUnit = 0.01
    upAxis = "Y"
)
def Xform "Plate" (
    kind = "component"
)
{
    def Mesh "Geom"
    {
        float3[] extent = [(-1, 0, -1), (1, 0, 1)]
        int[] faceVertexCounts = [4]
        int[] faceVertexIndices = [0, 1, 2, 3]
        point3f[] points = [(-1, 0, -1), (1, 0, -1), (1, 0, 1), (-1, 0, 1)]
        texCoord2f[] primvars:st = [(0, 0), (1, 0), (1, 1), (0, 1)] (
            interpolation = "vertex"
        )
        color3f[] primvars:displayColor = [(0.46, 0.72, 0)]
        custom float myStudio:wearAmount = 0.25
    }
}
\end{lstlisting}

\noindent Each line earns its place: \texttt{defaultPrim} makes the layer
referenceable; \texttt{metersPerUnit} and \texttt{upAxis} declare the
conventions consumers must honor; \texttt{kind = "component"} slots the asset
into the model hierarchy; \texttt{extent} is authored, not hoped for; the
\texttt{st} primvar carries UVs with explicit interpolation; and the
namespaced custom attribute carries studio data without inventing a schema.

\subsection{One format, three encodings}\label{sec:de-enc}\objref{4.3, 7.3}
\index{crate}\texttt{usda} and \texttt{usdc} (``crate'') encode the same scene
description. Crate is memory-mapped and lazily read --- opening a multi-GB
crate layer touches only the bytes composition needs --- and is the production
default. Text is greppable, diffable, and reviewable. Because \texttt{.usd}
may contain either encoding, conversion is just re-export:

\begin{lstlisting}[language=Python]
from pxr import Sdf, Usd

Sdf.Layer.FindOrOpen("asset.usda").Export("asset.usdc")

text  = Usd.Stage.Open("asset.usda")
crate = Usd.Stage.Open("asset.usdc")
path = "/Plate/Geom"
same = (text.GetPrimAtPath(path).GetAttribute("points").Get() ==
        crate.GetPrimAtPath(path).GetAttribute("points").Get())
print(same)   # True: same data, different container
\end{lstlisting}

\begin{ExamTip}
``What format is my \texttt{.usd} file?'' is a classic. The extension does not
say --- inspect it: \texttt{usdcat} prints any layer as text, and a crate file
starts with the magic bytes \texttt{PXR-USDC}. \texttt{usdz} is different
again: an \emph{uncompressed, 64-byte-aligned zip} that packages a default
layer plus its dependencies for delivery (think AR QuickLook), built with
\texttt{usdzip} --- you ship it, you don't edit it.
\end{ExamTip}

\subsection{The exporter skeleton: traversal}\label{sec:de-trav}\objref{4.7}
\index{traversal}Every exporter is the same loop: walk the composed stage,
recognize prims by schema, and map what you find onto the target format.

\begin{lstlisting}[language=Python]
from pxr import Usd, UsdGeom

stage = Usd.Stage.Open("asset.usda")
for prim in stage.Traverse():
    if prim.IsA(UsdGeom.Mesh):
        mesh = UsdGeom.Mesh(prim)
        print(prim.GetPath(),
              len(mesh.GetPointsAttr().Get()),
              list(mesh.GetFaceVertexCountsAttr().Get()))
# prints: /Plate/Geom 4 [4]
\end{lstlisting}

\begin{Gotcha}
\texttt{stage.Traverse()} visits the composed scenegraph but \textbf{does not
step inside instances}. If your export of an instanced scene comes out empty,
that is why: traverse with
\texttt{Usd.PrimRange(root, Usd.TraverseInstanceProxies())} (or de-instance
for export). The same trap bites validators.\index{instance proxy}
\end{Gotcha}

An importer is the mirrored loop --- read the foreign format, create prims,
set attributes --- with one extra decision that separates good pipelines from
destructive ones: \emph{author into a new layer, as \texttt{over}s where the
data refines something that already exists} (see Round-trip pipelines below).

\subsection{A real importer in 25 lines}\label{sec:de-importer}\objref{4.7, 4.8}
The skeleton becomes concrete with the smallest real format there is ---
Wavefront OBJ. Five lines of OBJ:

\begin{lstlisting}
v -1 -1 -1
v 1 -1 -1
v 1 1 -1
v -1 1 -1
f 1 2 3 4
\end{lstlisting}

\noindent And an importer that produces a \emph{clean} USD asset --- stage
metadata, computed extent and all, so it passes this chapter's own validator:

\begin{lstlisting}[language=Python]
from pxr import Usd, UsdGeom

points, counts, indices = [], [], []
for line in open("box.obj"):
    parts = line.split()
    if not parts:
        continue
    if parts[0] == "v":
        points.append(tuple(float(x) for x in parts[1:4]))
    elif parts[0] == "f":
        face = [int(p.split("/")[0]) - 1 for p in parts[1:]]
        counts.append(len(face))
        indices.extend(face)

stage = Usd.Stage.CreateNew("box_imported.usda")
mesh = UsdGeom.Mesh.Define(stage, "/Box")
stage.SetDefaultPrim(mesh.GetPrim())
UsdGeom.SetStageUpAxis(stage, UsdGeom.Tokens.y)
UsdGeom.SetStageMetersPerUnit(stage, 1.0)
mesh.GetPointsAttr().Set(points)
mesh.GetFaceVertexCountsAttr().Set(counts)
mesh.GetFaceVertexIndicesAttr().Set(indices)
mesh.GetExtentAttr().Set(UsdGeom.Boundable.ComputeExtentFromPlugins(
    mesh, Usd.TimeCode.Default()))
stage.Save()
\end{lstlisting}

\noindent Every exporter/importer question reduces to this shape: parse (or
emit) the foreign side, map onto schema attributes, declare the stage
conventions, author the extent. OBJ's 1-based face indices becoming USD's
0-based \texttt{faceVertexIndices} is the kind of mapping detail the
conceptual mapping document exists to record.

\subsection{Mapping USD to glTF (and friends)}\label{sec:de-map}\objref{4.1, 4.2}
Conversion quality is decided before any code is written --- in the
\emph{conceptual data mapping}: which concept on one side corresponds to
which on the other, and where information is lost.

\begin{figure}[ht]
  \centering
  \begin{tikzpicture}[node distance=2.2mm]
    \node[primbox, minimum width=3.4cm] (u1) {points};
    \node[primbox, minimum width=3.4cm, below=of u1] (u2) {faceVertexCounts/Indices};
    \node[primbox, minimum width=3.4cm, below=of u2] (u3) {primvars:st};
    \node[primbox, minimum width=3.4cm, below=of u3] (u4) {primvars:displayColor};
    \node[primbox, minimum width=3.4cm, below=of u4] (u5) {UsdPreviewSurface};
    \node[primbox, minimum width=3.4cm, below=of u5] (u6) {upAxis, metersPerUnit};
    \node[notetext, above=1.5mm of u1] {USD};
    \node[primbox, minimum width=3.4cm, right=34mm of u1] (g1) {POSITION};
    \node[primbox, minimum width=3.4cm, below=of g1] (g2) {indices (triangles only)};
    \node[primbox, minimum width=3.4cm, below=of g2] (g3) {TEXCOORD\_0};
    \node[primbox, minimum width=3.4cm, below=of g3] (g4) {COLOR\_0};
    \node[primbox, minimum width=3.4cm, below=of g4] (g5) {PBR metallic-roughness};
    \node[primbox, minimum width=3.4cm, below=of g5] (g6) {Y-up, meters (fixed)};
    \node[notetext, above=1.5mm of g1] {glTF};
    \draw[refArc] (u1) -- (g1);
    \draw[payArc] (u2) -- node[arcLabel] {triangulate} (g2);
    \draw[refArc] (u3) -- node[arcLabel] {rename} (g3);
    \draw[refArc] (u4) -- (g4);
    \draw[payArc] (u5) -- node[arcLabel] {approximate} (g5);
    \draw[payArc] (u6) -- node[arcLabel] {convert} (g6);
  \end{tikzpicture}
  \caption{A conceptual mapping at a glance. Solid arrows transfer cleanly;
  dashed arrows lose or transform information --- exactly what the mapping
  document must spell out.}
  \label{fig:gltf-map}
\end{figure}

The dashed arrows are where fidelity goes to die: glTF accepts only triangles
(USD n-gons must be triangulated --- topology changes), its coordinate system
is fixed Y-up/meters (convert or bake a corrective transform), and
UsdPreviewSurface only \emph{approximates} PBR metallic-roughness (document
which inputs survive). MaterialX mappings raise the same questions one level
up: node-graph topology, color spaces, and parameter defaults.\index{MaterialX}

\begin{DeepDive}
A useful conceptual data mapping document has five tables: (1) prim/schema
correspondences, (2) attribute-by-attribute mapping with types and units,
(3) defaults on each side when the other is silent, (4) named features that
do not survive (with the decision: drop, bake, or sidecar), and (5) naming
and namespace conventions. Write it before the exporter; review it like an
API contract --- that is precisely how the exam frames it.
\end{DeepDive}

\subsection{Round-trip pipelines}\label{sec:de-rt}\objref{4.4, 4.8, 7.4}
\index{round-trip}Export flattens: the target format has no notion of
references, variants, payloads, or layer offsets, so composition bakes into
plain data. The skill being examined is protecting the source of truth on the
way back in. The pattern: keep the original USD untouched, write the DCC's
changes into a \emph{new layer}, and author \texttt{over}s\index{over} ---
sparse opinions that refine existing prims --- rather than re-\texttt{def}ing
the world. Stronger-layer composition then merges the edit on top of the
original.

\begin{ExamTip}
``How do you import without destroying existing data?'' --- the answer is
some arrangement of: a separate layer for the import, \texttt{over} instead
of \texttt{def}, and composition (sublayer or reference) to combine. Any
answer that rewrites the original file is the distractor.
\end{ExamTip}

\subsection{Nonstandard data}\label{sec:de-nonstd}\objref{4.5, 3.6}
\index{custom attribute}\index{namespace}Data with no USD schema travels in
three ways, in increasing order of formality: \texttt{customData} metadata
(free-form dictionary, no time samples), \emph{namespaced custom attributes}
(\texttt{custom float myStudio:wearAmount} --- typed, sampled, queryable via
\texttt{GetPropertiesInNamespace}), and \emph{API schemas} generated with
\texttt{usdGenSchema}, which give the same data documented names, fallbacks,
and code-generated accessors (see the Customizing USD domain). Exporters
should read namespaces they own and ignore the rest; importers should
round-trip namespaces they do not understand instead of dropping them.

\subsection{Validating exports}\label{sec:de-val}\objref{4.6, 7.7}
Treat an export like a release artifact. Here is a deliberately broken one:

\begin{lstlisting}
#usda 1.0
def Mesh "Plate"
{
    int[] faceVertexCounts = [4]
    int[] faceVertexIndices = [0, 1, 2, 3]
    point3f[] points = [(-1, 0, -1), (1, 0, -1), (1, 0, 1), (-1, 0, 1)]
}
\end{lstlisting}

\noindent It parses, it even renders --- and it is wrong four ways: no
\texttt{defaultPrim}, no \texttt{upAxis}, no \texttt{metersPerUnit}, no
\texttt{extent}. The first three are caught mechanically:

\begin{lstlisting}[language=Python]
from pxr import UsdUtils

checker = UsdUtils.ComplianceChecker()   # the usdchecker engine
checker.CheckCompliance("bad_export.usda")
for failure in checker.GetFailedChecks():
    print(failure)
\end{lstlisting}

\noindent Three failures, all from \texttt{StageMetadataChecker}: the stage
does not specify \texttt{upAxis}, does not specify \texttt{metersPerUnit},
and has a missing or invalid \texttt{defaultPrim}. (Recent USD builds migrate
\texttt{usdchecker} to the new Validation Framework, flag
\texttt{--useNewValidationFramework}; the checks carry over.)

The missing \texttt{extent} is the exporter's own responsibility: bounds on
Boundables are \emph{authored}, not computed on demand, and renderers rely on
them. Compute and author in one move:\index{extent}

\begin{lstlisting}[language=Python]
from pxr import Usd, UsdGeom

stage = Usd.Stage.Open("bad_export.usda")
mesh = UsdGeom.Mesh(stage.GetPrimAtPath("/Plate"))
extent = UsdGeom.Boundable.ComputeExtentFromPlugins(
    mesh, Usd.TimeCode.Default())
mesh.GetExtentAttr().Set(extent)
print(extent)   # [(-1, 0, -1), (1, 0, 1)]
\end{lstlisting}

\begin{Gotcha}
Validation is also where material bindings go to fail quietly: a binding that
targets a prim \emph{outside} the \texttt{defaultPrim} hierarchy survives
every parser and dies only when the asset is referenced (Sample Question 12).
A good validator walks every \texttt{material:binding} and asserts the target
lives under \texttt{defaultPrim}.
\end{Gotcha}

\DrillsTitle
\subsection*{Drill 1: USDA vs USDC choice}
Write 4 situations where you would mandate one over the other.
\AnswerLines{7}
\begin{DrillSolution}
(1) Code review / version-control diffs of small handwritten layers
$\Rightarrow$ usda. (2) Production caches, heavy geometry, anything opened at
scale $\Rightarrow$ usdc (memory-mapped, lazy). (3) Teaching, debugging a
composition problem, minimal repros $\Rightarrow$ usda. (4) Delivery to a
consumer device or AR viewer $\Rightarrow$ usdz packaging the usdc payload.
\end{DrillSolution}

\subsection*{Drill 2: Validator checklist}
List 10 checks your exporter should run before shipping an asset.
\AnswerLines{10}
\begin{DrillSolution}
(1) Layer opens with no warnings on stderr. (2) \texttt{defaultPrim} set and
valid. (3) \texttt{upAxis} declared. (4) \texttt{metersPerUnit} declared.
(5) Every Boundable has an authored \texttt{extent}. (6) Topology consistent:
$\sum$\texttt{faceVertexCounts} $=$ \texttt{len(faceVertexIndices)}, indices
in range of \texttt{points}. (7) Material bindings target prims under
\texttt{defaultPrim}. (8) Primvar interpolation matches element counts.
(9) Asset paths resolve (no absolute local paths). (10) Naming/namespace
conventions hold; unknown namespaces preserved, not dropped.
\end{DrillSolution}

\subsection*{Drill 3: glTF fidelity risks}
Name 4 ways a USD$\rightarrow$glTF conversion silently loses fidelity, and
the mitigation for each.
\AnswerLines{7}
\begin{DrillSolution}
(1) N-gons triangulated $\Rightarrow$ export consistent winding/normals and
validate visually. (2) Up-axis/units differ $\Rightarrow$ convert vertices or
bake one corrective root transform, never both. (3) Materials approximated
$\Rightarrow$ document which UsdPreviewSurface inputs map to PBR
metallic-roughness and bake the rest to textures. (4) Primvars renamed or
dropped (\texttt{st} $\rightarrow$ \texttt{TEXCOORD\_0}, extra UV sets,
\texttt{displayColor}) $\Rightarrow$ explicit mapping table in the conceptual
mapping document.
\end{DrillSolution}

\subsection*{Drill 4: Non-destructive import design}
Sketch the layer/composition design for importing a DCC edit of an existing
USD asset without touching the original.
\AnswerLines{6}
\begin{DrillSolution}
New layer per import session; the importer authors \texttt{over}s on the
existing prim paths (and \texttt{def}s only for genuinely new prims); the
shot stage sublayers (or references) the import layer \emph{above} the
original so its opinions win; the original asset file is never reopened for
writing. Bonus: record provenance in \texttt{customData}.
\end{DrillSolution}

\section*{Checkpoint Questions}
\addcontentsline{toc}{section}{Checkpoint Questions}

\noindent\textbf{CQ1.} One asset must be (a) reviewed line-by-line in a PR,
(b) loaded fast in production, (c) delivered to an AR viewer. Which encoding
each time?
\begin{DrillSolution}
(a) usda --- text diffs; (b) usdc --- memory-mapped crate; (c) usdz --- the
zip delivery package (containing crate data).
\end{DrillSolution}

\noindent\textbf{CQ2.} Your exporter reports zero meshes on a scene full of
instanced buildings. Why, and what is the fix?
\begin{DrillSolution}
\texttt{Traverse()} does not descend into instances. Traverse with
\texttt{Usd.PrimRange(root, Usd.TraverseInstanceProxies())}, or de-instance
for export. The data was always there --- the iterator skipped it.
\end{DrillSolution}

\noindent\textbf{CQ3.} Who is responsible for \texttt{extent}, and which API
computes it?
\begin{DrillSolution}
The authoring side --- whoever wrote the points. Bounds are authored data,
not derived on demand:
\texttt{UsdGeom.Boundable.ComputeExtentFromPlugins(boundable, time)}, then
\texttt{GetExtentAttr().Set(...)}. Update it whenever points change (compare
Sample Question 5).
\end{DrillSolution}

\subsection*{Mini-checklist (tick when mastered)}
\begin{itemize}[leftmargin=*]
  \item[$\square$] I can tell what is inside a \texttt{.usd} file without trusting the extension.
  \item[$\square$] I can write the traversal loop of an exporter from memory --- including the instancing trap.
  \item[$\square$] I can name the lossy edges of a USD$\rightarrow$glTF mapping before writing code.
  \item[$\square$] I can design an import that leaves the original asset byte-identical.
  \item[$\square$] I can list what \texttt{usdchecker} catches --- and what stays my job (\texttt{extent}).
\end{itemize}
