\clearpage
\section*{Answer Key and Domain Scoring}
\addcontentsline{toc}{section}{Answer Key and Domain Scoring}
\label{ch:mockkey}

Score one point per correct answer, then total each domain row below ---
the same per-domain readout Certiverse gives you, so a weak row tells you
which chapter to revisit. (Domain sizes approximate the official weights.)
Composition scenario answers in this key are verified by this book's test
suite.

\begin{center}
\begin{tabular}{@{}p{1.75in}p{2.0in}p{0.55in}@{}}
\textbf{\sffamily Domain (chapter)} & \textbf{\sffamily Questions} & \textbf{\sffamily /total} \\[2pt]
Composition (\S3) & 1, 3, 10, 11, 12, 13, 18, 25, 41, 42, 52, 57 & /12 \\
Data Exchange (\S6) & 2, 4, 15, 24, 30, 31, 35, 47, 51 & /9 \\
Data Modeling (\S7) & 6, 17, 23, 33, 34, 45, 48, 49, 56 & /9 \\
Debugging (\S8) & 7, 14, 20, 29, 36, 46, 50 & /7 \\
Content Aggregation (\S4) & 8, 19, 26, 32, 40, 54 & /6 \\
Visualization (\S10) & 9, 27, 37, 38, 44, 58 & /6 \\
Pipeline Development (\S9) & 5, 21, 22, 43, 53, 55 & /6 \\
Customizing USD (\S5) & 16, 28, 39, 59 & /4 \\
Exam craft & 60 & /1 \\
\end{tabular}
\end{center}

\subsection*{Answers}

\noindent\textbf{1. A} --- Local, Inherits, VariantSets, References,
Payload, Specializes. B is the classic wrong expansion (sublayers are
\emph{Local}); the others scramble letters.

\noindent\textbf{2. D} --- the extension does not commit to an encoding;
\texttt{usdcat} (or the \texttt{PXR-USDC} magic bytes) reveals it.

\noindent\textbf{3. C} --- the root layer's own opinion is the strongest
Local opinion, above both sublayers; 6 wins. Verified by composition in the
test suite.

\noindent\textbf{4. C} --- \texttt{Traverse()} skips instance contents;
traverse with instance proxies (or de-instance for export).

\noindent\textbf{5. D} --- the model hierarchy must be contiguous: a
component under a plain prim reports \texttt{IsModel() == False} (verified
in \S9). A is therefore false; subcomponents are not models; nothing
validates kinds at save time.

\noindent\textbf{6. C} --- metadata (including \texttt{customData} and
\texttt{assetInfo}) is never time-sampled; time-varying values live in
attributes.

\noindent\textbf{7. C} --- muting removes the layer from composition,
in-session and reversibly: the bisection tool.

\noindent\textbf{8. D} --- proxies exist for reading; authoring raises
\texttt{Tf.ErrorException} (verified in \S4).

\noindent\textbf{9. A} --- a \texttt{float3} primvar reader with
\texttt{varname = "displayColor"} feeding \texttt{diffuseColor}. B reads
a texture; D reads UVs; C connects nothing a surface output understands.

\noindent\textbf{10. A} --- \texttt{defaultPrim} answers ``what composes
when this layer is referenced/payloaded without a prim path''.

\noindent\textbf{11. C} --- stage time $=$ source $\times$ scale $+$ offset
$= 10 \times 2 + 20 = 40$.

\noindent\textbf{12. D} --- flatten bakes composition and strips internal
structure; \texttt{usdzip} packages dependencies for travel.

\noindent\textbf{13. A} --- within one arc class, earlier list entries are
stronger; \texttt{propA}'s red wins. Verified by composition in the test
suite.

\noindent\textbf{14. C} --- ChangeBlock coalesces many small edits into one
round of change processing; it does nothing for single edits and is wrong
around composed reads.

\noindent\textbf{15. C} --- usdz: uncompressed, 64-byte-aligned zip,
delivery-oriented, not an editing format.

\noindent\textbf{16. D} --- kinds are registered vocabulary: plugInfo
discovered via \texttt{PXR\_PLUGINPATH\_NAME}, on every site that consumes
the assets. (This book's tests register one in a subprocess to prove the
flow.)

\noindent\textbf{17. C} --- uniform means one value per \emph{face}; one
face, three values: invalid. Constant wants one value total (A's reasoning
is wrong); vertex wants one per point, which 4 satisfies.

\noindent\textbf{18. B} --- the default load policy is \texttt{LoadAll};
deferral is opt-in via \texttt{LoadNone}/\texttt{Load()}.

\noindent\textbf{19. A} --- edit what the prototype composes from and every
instance follows; per-instance edits require de-instancing (and C's
``all instances'' defeats instancing wholesale).

\noindent\textbf{20. D} --- strongest first; the top spec is the opinion the
stage returns.

\noindent\textbf{21. C} --- the asset interface pattern: stable thin entry
point, heavy contents deferrable behind the payload, versions repointable
without touching consumers.

\noindent\textbf{22. A} --- \texttt{GetCompositionAssetDependencies()}
returns exactly the sublayer/reference/payload asset paths; the gate checks
them for absolute paths and backslashes.

\noindent\textbf{23. B} --- token is for closed vocabularies; text wants
\texttt{string}, paths want \texttt{asset}, prim pointers want \texttt{rel}.

\noindent\textbf{24. D} --- the stage-metadata rules report three failures:
missing \texttt{upAxis}, missing \texttt{metersPerUnit}, missing/invalid
\texttt{defaultPrim} (this book runs the checker on exactly this case).

\noindent\textbf{25. A} --- I sits above V; S sits at the very bottom:
inherits broadcasts with strength, specializes is the never-winning
fallback.

\noindent\textbf{26. A} --- list position is the index: the appended
prototype is index 2.

\noindent\textbf{27. B} --- purpose tags subtrees for consumers; proxy
draws in interactive viewports, render in final frames, and
\texttt{default} everywhere.

\noindent\textbf{28. C} --- per-release C++ ABI: same version, same
toolchain, or the plug-in silently fails to load
(\texttt{TF\_DEBUG=PLUG\_REGISTRATION} shows why).

\noindent\textbf{29. B} --- the property stack \emph{is} the provenance
answer; everything else is archaeology.

\noindent\textbf{30. D} --- foreign formats hold flat data; arcs, variants,
payloads, and offsets bake away. Protecting the source of truth is pipeline
design (overs + layers).

\noindent\textbf{31. C} --- new layer, sparse \texttt{over}s, composed above
the original; the original file is never rewritten.

\noindent\textbf{32. B} --- per-instance half-precision quaternions, real
part first (one entry per instance, like every PointInstancer array).

\noindent\textbf{33. C} --- Default-time queries read the default value;
samples answer only timed queries. The classic ``works in usdview, empty in
my script'' bug.

\noindent\textbf{34. B} --- held interpolation returns the previous sample:
1. (Linear would give 6; both verified in \S7's listing.)

\noindent\textbf{35. D} --- same scene description, different container:
crate is memory-mapped and lazy; text is greppable and diffable.

\noindent\textbf{36. B} --- plugin discovery problems are invisible without
it; the other options have their own tools.

\noindent\textbf{37. C} --- one material + per-prim primvars keeps sharing
intact; unique networks per instance fork prototypes (the instancing-breaker
list).

\noindent\textbf{38. D} --- subsets store face \emph{indices}; topology
edits silently re-target them. Validate subsets after any
topology-touching step.

\noindent\textbf{39. B} --- codeless schemas deploy as data: no
compilation, no ABI coupling; generated accessors are the trade-away.

\noindent\textbf{40. B} --- full prim identity at moderate counts is
scenegraph instancing's home turf; PointInstancer trades identity for
array scale.

\noindent\textbf{41. A} --- it makes the layer referenceable without an
explicit prim path --- publish-time hygiene.

\noindent\textbf{42. D} --- the namespace question decides it: same prims
$\Rightarrow$ sublayers; graft under a new path $\Rightarrow$ reference.

\noindent\textbf{43. B} --- bindings that target outside
\texttt{defaultPrim} survive parsing and die on reference (Sample
Question 12's trap, automated).

\noindent\textbf{44. C} --- visibility inherits down namespace; an
\texttt{invisible} ancestor hides the subtree (verified in \S10's listing).

\noindent\textbf{45. A} --- application is recorded in \texttt{apiSchemas}
metadata; \texttt{HasAPI} is the cheap query (verified in \S5's listing).

\noindent\textbf{46. A} --- mute, observe, unmute: composition re-resolves
each time; that is what makes it a bisection tool.

\noindent\textbf{47. D} --- triangulation plus axis/unit conversion are the
two structural fidelity costs; the material model is approximated, not
shared.

\noindent\textbf{48. A} --- canonical TRS authoring/reading without
hand-managing \texttt{xformOpOrder}.

\noindent\textbf{49. B} --- \texttt{asset} is the type resolvers and
dependency walkers see; a \texttt{string} path is invisible to both.

\noindent\textbf{50. D} --- the textbook ChangeBlock case: thousands of
small writes, one recomposition; reads stay outside the block.

\noindent\textbf{51. A} --- the file-format plug-in interface is exactly how
USD's own formats are registered; foreign formats join the same way.

\noindent\textbf{52. B} --- selections compose by strength like any opinion;
Local beats variant-authored. (Sample Question 13, verified by
composition.)

\noindent\textbf{53. B} --- counts/indices split plus the 1-based to
0-based shift --- the exact mapping detail the chapter's OBJ importer
implements.

\noindent\textbf{54. D} --- invisibleIds is per-instance, cheap, reversible
hiding; arrays stay untouched (the render in \S4 shows the gap).

\noindent\textbf{55. B} --- resolvers locate; they never parse or create
content (that is file formats and SceneIndex respectively).

\noindent\textbf{56. A} --- roles carry semantics: points transform with
translation, vectors do not, colors get color management.

\noindent\textbf{57. B} --- warnings on stderr are composition errors in
disguise; pipelines fail on them at publish, where the fix is cheap.

\noindent\textbf{58. C} --- \texttt{LightAPI} owns the shared dials
(intensity, color, exposure); \texttt{angle} belongs to DistantLight,
camera properties to cameras.

\noindent\textbf{59. B} --- typed-and-documented data on \emph{existing}
prim types across shows is the applied-API-schema case; customData has no
fallbacks or validation, and a new typed schema is the wrong granularity.

\noindent\textbf{60. A} --- ninety seconds per question on average:
eliminate fast, mark, return. Time pressure, not difficulty, is the
most-reported failure mode.
